Download data

### 2023-12-07 scripts/download_dependent_variables.Rmd
fn to select newest record per cell

idig <- read.csv(file.path(base_p, 'IDIG.csv')) %>% 
  st_as_sf(coords = c('geopoint.lon', 'geopoint.lat'), crs = 4326) %>% 
  mutate(date = as.Date(datecollected)) %>% 
  select(taxon = scientificname)

aim <- st_read(file.path(base_p, 'AIM', 'AIM_records.shp')) %>% 
  mutate(date = as.Date(DatVstd)) %>% 
  select(taxon, date) %>% 
  st_transform(4326)

gbif1 <- read.delim(file.path(base_p, 'gbif1', 'occurrence.txt'), na.strings = "") # %>% 
  drop_na(decimalLongitude, decimalLatitude) %>% 
  filter(str_detect(decimalLatitude, '[A-Z]|[a-z]', negate = T)) %>% 
  st_as_sf(coords = c('decimalLongitude', 'decimalLatitude'), crs = 4326) %>% 
  mutate(date = as.Date(eventDate), .before = geometry, 
         coordinateUncertaintyInMeters = as.numeric(coordinateUncertaintyInMeters)) %>% 
  filter(coordinateUncertaintyInMeters <= 250) %>% 
  select(taxon = species, date)

@@

records <- st_transform(records, 5070)
splicies <- split(records, records$taxon)[1:2]

splicies <- lapply(splicies, st_buffer, dist = 90)
st_buffer(x, dist = 90)

@@

  dists <- sf::st_distance(x)
}

test <- st_intersects(splicies[[1]])

test1 <- test[ lengths(test) > 1 ]
untest <- unique(test1)

sum( lengths(test)  > 1 ) # 637 records
sum( lengths(test) == 2 ) # 285 records dupe in paired, 142 records...
sum( lengths(test)  > 3 )

test <- test[sum(lengths(test)  > 1 )]

out <- unique(test)

# identify each

# find records < 90m distance

@@

>>>>

idig <- read.csv(file.path(base_p, 'IDIG.csv')) %>% 
  st_as_sf(coords = c('geopoint.lon', 'geopoint.lat'), crs = 4326) %>% 
  mutate(date = as.Date(datecollected)) %>% 
  select(taxon = scientificname, date)

aim <- st_read(file.path(base_p, 'AIM', 'AIM_records.shp'), quiet = TRUE) %>% 
  mutate(date = as.Date(DatVstd)) %>% 
  select(taxon, date) %>% 
  st_transform(4326)

gbif1 <- read.delim(file.path(base_p, 'gbif1', 'occurrence.txt'), na.strings = "") %>% 
  drop_na(decimalLongitude, decimalLatitude) %>% 
  filter(str_detect(decimalLatitude, '[A-Z]|[a-z]', negate = T)) %>% 
  st_as_sf(coords = c('decimalLongitude', 'decimalLatitude'), crs = 4326) %>% 
  mutate(date = as.Date(eventDate), .before = geometry, 
         coordinateUncertaintyInMeters = as.numeric(coordinateUncertaintyInMeters)) %>% 
  filter(coordinateUncertaintyInMeters <= 250) %>% 
  select(taxon = species, date)

@@

splicies <- split(records, records$taxon)[1:10]

@@

  records <- sf::st_transform(x, 5070) |>
    sf::st_buffer( dist = 90)

  intersects <- sf::st_intersects(records)
  intersect_sets <- unique(intersects) # identify intersected points

  records_list <- vector(mode = 'list', length = length(intersect_sets))
  for (i in seq_along(intersect_sets)){
    records_list[[i]] <- records[unlist((intersect_sets[i])),]
  }

  records_list <- bind_rows(
    lapply(records_list, function(x) x[which.max(x$date),])
  )

  return(records_list)

}

out <- lapply(splicies, ONEperCELL)

@@

```{r}
multiplesPERcell <- function(x){

  records <- sf::st_transform(x, 5070) |>
    sf::st_buffer( dist = 90)

  intersects <- sf::st_intersects(records)
  intersect_sets <- unique(intersects) # identify intersected points

  records_list <- vector(mode = 'list', length = length(intersect_sets))
  for (i in seq_along(intersect_sets)){
    records_list[[i]] <- records[unlist((intersect_sets[i])),]
  }

  max <- bind_rows(
    lapply(records_list, function(x) x[which.max(x$date),])
  )

}
```
